Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach

### 2021-04-27 analysis/paper/asymsam.Rmd
Agrega comentarios sobre onda 3 en S-SAM
#18

<!-- ```{r} -->

<!-- indices_wide %>%  -->

<!--   .[, FitLm(as.numeric(time), asym, sym, se = TRUE), by = .(lev)] %>%  -->

<!--   rm_intercept() %>%  -->

<!--   # .[, term := NULL] %>%  -->

<!--   .[, estimate := estimate/(3600*24*365*10)] %>% -->

<!--   .[, std.error := std.error/(3600*24*365*10)] %>% -->

<!--   # setnames("type", "term") %>%  -->

<!--   ggplot(aes(lev, estimate)) + -->

<!--   geom_ribbon(aes(ymax = estimate + std.error*1.96, ymin = estimate - std.error*1.96), alpha = 0.3) + -->

<!--   geom_line() + -->

<!--   scale_fill_brewer(palette = "Dark2", aesthetics = c("color", "fill")) + -->

<!--   geom_hline(yintercept = 0) + -->

<!--   scale_x_level() + -->

<!--   scale_y_continuous("Standard deviations per decade") + -->

<!--   coord_flip() + -->

<!--   facet_grid(~ term,labeller = labeller(term = lab_sam)) + -->

<!--   tag_facets()  -->

<!-- ``` -->

@@

In the troposphere, the regression pattern associated with the SAM shows the well-known combination of zonally symmetrical annular mode with zonal asymmetries in the form of a wave-3 (Figure \@ref(fig:2d-regr)a.2, [@fogt2012]).
The regression patterns associated with the A\nobreakdash-SAM and S\nobreakdash-SAM indices successfully disentangle both structures.
While the A\nobreakdash-SAM index gives rise to a cleaner zonal wave (Figure \@ref(fig:2d-regr)b.2), the S\nobreakdash-SAM index is associated with an annular structure, almost devoid of zonal asymmetries (Figure \@ref(fig:2d-regr)c.2).
The wave-3 pattern observed in Figure \@ref(fig:2d-regr)b.2 is rotated by half a wavelength from the average position of the mean wave-3 pattern described by @raphael2004, whose reference locations are marked with points in the figure.
Indeed, there is no correlation between @raphael2004's index and A\nobreakdash-SAM (cor = `r signif(cor_raphael$estimate, 2)`, p-value `r report_p(cor_raphael$p.value)`).
Thus, the tropospheric A\nobreakdash-SAM index represents a zonal displacement in the position of the climatological wave-3 pattern.

>>>>

@@

In the troposphere, the regression pattern associated with the SAM shows the well-known combination of zonally symmetrical annular mode with zonal asymmetries in the form of a wave-3 (Figure \@ref(fig:2d-regr)a.2, [@fogt2012]).
The regression patterns associated with the A\nobreakdash-SAM and S\nobreakdash-SAM indices successfully disentangle both structures.
While the A\nobreakdash-SAM index gives rise to a cleaner zonal wave (Figure \@ref(fig:2d-regr)b.2), the S\nobreakdash-SAM index is associated with an annular structure, with only vestigial zonal asymmetries (Figure \@ref(fig:2d-regr)c.2) in the shape of a wave-3 which is the inverse of the A\nobreakdash-SAM wave-3.
The wave-3 pattern observed in Figure \@ref(fig:2d-regr)b.2 is rotated by half a wavelength from the average position of the mean wave-3 pattern described by @raphael2004, whose reference locations are marked with points in the figure.
Indeed, there is no correlation between @raphael2004's index and A\nobreakdash-SAM (cor = `r signif(cor_raphael$estimate, 2)`, p-value `r report_p(cor_raphael$p.value)`).
Thus, the tropospheric A\nobreakdash-SAM index represents a zonal displacement in the position of the climatological wave-3 pattern.
